The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-17 paper/ms.tex
added variability analysis

\subsubsection{Classical Pulsators}
\label{pulsators}

@@

\subsubsection{Eclipsing Binaries}
\label{ebs}

>>>>

For all the main sequence stars in our sample, we visually inspected light curves and power spectra to determine their variability class. In the following subsections, we will briefly comment on some of the findings. As main sequence variables are so diverse, and suited to varied science cases, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.

\subsubsection{Classical Pulsators}
\label{pulsators}
The sample contains many $\delta\,\text{Sct}$ and $\gamma\,\text{Dor}$ variables, and several hybrid pulsators. \textcolor{red}{Simon - add text here.}
Including hotter stars, we also detect SPB pulsations in \textcolor{red}{some stars - Conny/Tim van Reeth?}.

\subsubsection{Hump and Spike Stars}
\label{hs}

@@

\subsubsection{Eclipsing Binaries}
\label{ebs}
We detect some eclipsing binaries \textcolor{red}{Ben - finish this.}
